Making all equalities equal

### 2021-09-20 paper.lagda.tex
joined equalities
changed to module versioned

>>>>

\begin{code}
module Equalities {a ℓ} {A : Set a} where
  ≣-Type' = ≣-Type {a} {ℓ} {A}
  open IsEquality

  module _
    (_≡₁_ : ≣-Type')
    (_≡₂_ : ≣-Type')
    ⦃ eq₁ : IsEquality {a} {ℓ} _≡₁_ ⦄
    ⦃ eq₂ : IsEquality _≡₂_ ⦄
    where

    variable
      x y : A

    alwaysEqual :  x ≡₁ y → x ≡₂ y
    alwaysEqual p =
      let joined = eq₁ .≣-≡-≡ ∙ sym (eq₂ .≣-≡-≡)
      in transport joined p

\end{code}
